Storm Surges

### 2014-07-05 RoughWork/manuscript.tex
Added comment aout surge statistics

Model results have been compared with observations by calculating both the total modelled water level and the modelled residual. . The modelled residual is calculated as the difference in model output between a simulation with all forcing conditions and a simulation forced only with tides and rivers. The observed water level is taken from observations by Fisheries and Oceans Canada (citation) and the observed residual is the observations minus tidal predictions. Tidal predictions are calculated using t\_tide \cite{pawlowicz2002classical}, a MATLAB tool that calculates tidal harmonics from a given time series, in this cae, from the year prior surge event on interest.

@@

The error in modelled residuals at Victoria and Campbell River is also apparent in these figures. Most noticebale is underestimate in modelled residual throughout most of the time period. Additionally, there is a delay of about 2-3 hours in the timing of maximum residual at most locations and the  relative errors in maximum residual range from 5\% at Point Atkinson to 29\% at Patricia Bay. 
%Question: is it better to present relative errors or just difference?

>>>>

Model results have been compared with observations by calculating both the total modelled water level and the modelled residual. . The modelled residual is calculated as the difference in model output between a simulation with all forcing conditions and a simulation forced only with tides and rivers. The observed water level is taken from observations by Fisheries and Oceans Canada (citation) and the observed residual is the observations minus tidal predictions. Tidal predictions are calculated using t\_tide \citep{pawlowicz2002classical}, a MATLAB tool that calculates tidal harmonics from a given time series, in this cae, from the year prior surge event on interest.

@@

The error in modelled residuals at Victoria and Campbell River is also apparent in these figures. Most noticebale is underestimate in modelled residual throughout most of the time period. Additionally, there is a delay of about 2-3 hours in the timing of maximum residual at most locations and the  relative errors in maximum residual range from 5\% at Point Atkinson to 29\% at Patricia Bay. 
%Question: is it better to present relative errors or just difference?
%I think Hal Ritchie's talk with the storm surges had some stats presented. Look this up...
